---
title: "Quiz Practice"
author: "Han"
date: "3/14/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### Data Import and Cleaning : import, remove NAs and stable columns
```{r}
library("caret")
Urltrain <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
Urltest <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

Train1 <- read.csv(Urltrain, header = TRUE, na.strings = c("NA","#DIV/0!", ""))
str(Train1)
Test <- read.csv(Urltest, header = TRUE,na.strings = c("NA","#DIV/0!", ""))
str(Test)

NearOVar <- nearZeroVar(Train1)
Train2 <-Train1[, - NearOVar]
Test2 <- Test[, - NearOVar]

ValidColIndex <- colSums(is.na(Train2)/nrow(Train2)) < 0.95
Train3 <-Train2[,ValidColIndex]
Test3 <-Test2[,ValidColIndex]
str(Train3)

Index <- as.numeric()
for (i in 1:5) {
  relatedstrings <- c("belt", "arm", "forearm", "dumbbell", "classe")
  Index <- unique(c(Index, grep(relatedstrings[i], colnames(Train3))))
}
Train_data <- Train3[, Index]
Test_data <- Test3[, Index]
str(Train_data)
```

### Decission Tree Model
```{r}
library("rpart")
library("rpart.plot")
library("e1071")

set.seed(2333)
Train_data_Train_Index <- createDataPartition(Train_data$classe, p = 0.75, list = FALSE)
Train_data_Train <- Train_data[Train_data_Train_Index,]
Train_data_Test <- Train_data[-Train_data_Train_Index,]

dTree <- train(classe ~., method = "rpart", data = Train_data)
dTree
rpart.plot(dTree$finalModel)

Train_data_Prediction <- predict(dTree, Train_data_Test)
confusionMatrix(Train_data_Test$classe, Train_data_Prediction)
```
rpart decision tree could only give 0.49 accuracy as evaluated by confusionMatrix


### Random Forrest
```{r}
rForrest <- train(classe ~., method = "rf", data = Train_data, ntree = 128)
Train_data_Prediction <- predict(rForrest, Train_data_Test)
confusionMatrix(Train_data_Test$classe, Train_data_Prediction)
```
As the confusion Matrix indicated, random forest model could give better acurracy than rpart method, so the model trained through random forest would be used for testing data

```{r}
Test_data_Prediction <- predict(rForrest, Test_data)
Test_data_Prediction
```
